\PaperTitle

### 2024-05-05 Final_Report/paper.tex
Spellcheck

  A thorough evaluation of the models was conducted through testing and validation sets, hyperparameter optimization employing cross-validation and grid search, and computing accuracy and Macro F1 scores. The results showed that the Neural Network model 
  acheived the highest accuracy of $85\%$ and Macro F1 score of 84.

@@

Variables $w_i$ and $b$ correspond to weight and bias, respectivly. Both of these terms get set by the training process of the model, which we'll discuss shortly. 
The resulting value, $z$, is the input to an {\it activation function}, which, depending on which is used, modifies and normalizes the output before it is passed to the next node.

>>>>

  A thorough evaluation of the models was conducted through testing and validation sets, hyperparameter optimization employing cross-validation and grid search, and computing accuracy and Macro F1 scores. The results showed that the Neural Network model 
  achieved the highest accuracy of $85\%$ and Macro F1 score of 84.

@@

Variables $w_i$ and $b$ correspond to weight and bias, respectively. Both of these terms get set by the training process of the model, which we'll discuss shortly. 
The resulting value, $z$, is the input to an {\it activation function}, which, depending on which is used, modifies and normalizes the output before it is passed to the next node.
